Regime-Specific Performance of 1D CNN and FCNN Architectures for Non-linear Matter Power Spectrum Emulation in LCDM Cosmology

### 2025-05-02 Project4/paper_v2.tex
fix: Correct image paths in paper_v2.tex to be relative to Project4
Refactor: Improve clarity and consistency in paper text.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/error_vs_k_cnn1d_3_1745408317.png}
    \caption{\label{fig:error_vs_k_cnn1d}The relative error $\Delta P/P$ as a function of the wavenumber $k$ for a 1D CNN. The median error is shown as a solid blue line, and the 68\% confidence interval is shown as a shaded blue region. Large differences are observed around $\log_{10} k \sim -1$, where the median relative error oscillates significantly.}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/error_vs_k_fcnn_4_1745408320.png}
    \caption{\label{fig:error_vs_k_fcnn}Relative error between the predicted power spectrum from a fully connected neural network (FCNN) and the true power spectrum, as a function of wavenumber $k$. The solid line shows the median relative error, while the shaded region indicates the 68\% confidence interval. The relative error is small at low $k$ but increases significantly at high $k$. Oscillations are seen around $k \sim 10^{-1} \, h/\mathrm{Mpc}$.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/error_vs_z_cnn1d_5_1745408323.png}
    \caption{\label{fig:error_vs_z_cnn1d}The figure shows the relative error in the power spectrum, $\Delta P/P$, as a function of redshift, $z$, for different $k$-regimes: linear, quasi-linear, and non-linear. The relative error is the median value across the scales. The linear regime shows a decreasing trend with increasing redshift. The quasi-linear regime shows a slightly increasing trend with redshift. The non-linear regime shows a decreasing trend with redshift.}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/error_vs_z_fcnn_6_1745408327.png}
    \caption{\label{fig:error_vs_z_fcnn}Relative error in the power spectrum ($\Delta P/P$) as a function of redshift ($z$) for different $k$-regimes (linear, quasi-linear, and non-linear) using a Fully Convolutional Neural Network (FCNN). The linear regime shows the smallest relative error, remaining consistently below 0.003 across all redshifts. The quasi-linear regime exhibits the largest errors, peaking around $z=0.6$.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/true_vs_emulated_cnn1d_1_1745408311.png}
    \caption{\label{fig:true_vs_emulated_cnn1d}Comparison of the true and emulated power spectrum, $P(k)$, for different redshifts, $z$. The emulated $P(k)$ is obtained using a 1D Convolutional Neural Network (CNN). The plots show the logarithm of the power spectrum, $\log_{10} P(k)$, as a function of the logarithm of the wavenumber, $\log_{10} k$. The true and emulated power spectra are in good agreement, with only small differences observed across the range of wavenumbers and redshifts shown.}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/true_vs_emulated_fcnn_2_1745408315.png}
    \caption{\label{fig:true_vs_emulated_fcnn}The figure shows the comparison between the true and emulated power spectrum, $P(k)$, at different redshifts ($z=0.17, 0.28, 0.80, 0.45$). The black solid line represents the true power spectrum, while the orange dashed line represents the emulated power spectrum obtained using a Fully Convolutional Neural Network (FCNN). Small differences are found between the true and emulated power spectra at all redshifts.}
\end{figure}

@@

\bibliography{bibliography}
\bibliographystyle{aasjournal}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project4/plots/error_vs_k_cnn1d_3_1745408317.png}
    \caption{\label{fig:error_vs_k_cnn1d}The relative error $\Delta P/P$ as a function of the wavenumber $k$ for a 1D CNN. The median error is shown as a solid blue line, and the 68\% confidence interval is shown as a shaded blue region. Large differences are observed around $\log_{10} k \sim -1$, where the median relative error oscillates significantly.}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project4/plots/error_vs_k_fcnn_4_1745408320.png}
    \caption{\label{fig:error_vs_k_fcnn}Relative error between the predicted power spectrum from a fully connected neural network (FCNN) and the true power spectrum, as a function of wavenumber $k$. The solid line shows the median relative error, while the shaded region indicates the 68\% confidence interval. The relative error is small at low $k$ but increases significantly at high $k$. Oscillations are seen around $k \sim 10^{-1} \, h/\mathrm{Mpc}$.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project4/plots/error_vs_z_cnn1d_5_1745408323.png}
    \caption{\label{fig:error_vs_z_cnn1d}The figure shows the relative error in the power spectrum, $\Delta P/P$, as a function of redshift, $z$, for different $k$-regimes: linear, quasi-linear, and non-linear. The relative error is the median value across the scales. The linear regime shows a decreasing trend with increasing redshift. The quasi-linear regime shows a slightly increasing trend with redshift. The non-linear regime shows a decreasing trend with redshift.}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project4/plots/error_vs_z_fcnn_6_1745408327.png}
    \caption{\label{fig:error_vs_z_fcnn}Relative error in the power spectrum ($\Delta P/P$) as a function of redshift ($z$) for different $k$-regimes (linear, quasi-linear, and non-linear) using a Fully Convolutional Neural Network (FCNN). The linear regime shows the smallest relative error, remaining consistently below 0.003 across all redshifts. The quasi-linear regime exhibits the largest errors, peaking around $z=0.6$.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project4/plots/true_vs_emulated_cnn1d_1_1745408311.png}
    \caption{\label{fig:true_vs_emulated_cnn1d}Comparison of the true and emulated power spectrum, $P(k)$, for different redshifts, $z$. The emulated $P(k)$ is obtained using a 1D Convolutional Neural Network (CNN). The plots show the logarithm of the power spectrum, $\log_{10} P(k)$, as a function of the logarithm of the wavenumber, $\log_{10} k$. The true and emulated power spectra are in good agreement, with only small differences observed across the range of wavenumbers and redshifts shown.}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project4/plots/true_vs_emulated_fcnn_2_1745408315.png}
    \caption{\label{fig:true_vs_emulated_fcnn}The figure shows the comparison between the true and emulated power spectrum, $P(k)$, at different redshifts ($z=0.17, 0.28, 0.80, 0.45$). The black solid line represents the true power spectrum, while the orange dashed line represents the emulated power spectrum obtained using a Fully Convolutional Neural Network (FCNN). Small differences are found between the true and emulated power spectra at all redshifts.}
\end{figure}

@@

\bibliography{bibliography}{}
\bibliographystyle{aasjournal}
